Irt plot extra

### 2022-05-23 manuscript.Rmd
Typo fixed

A quantitative cross-sectional fully anonymous geographically unconstrained online large-scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic-book "Enlighten your clock" co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux]. The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation any time without being penalized. At the beginning of the survey, for the adult participants (\>18 years) consent was recorded digitally. Under-aged participants (\<18 years) were urged to obtain assent from their parents/legal guardians. The entire survey was estimated to take less than 30 minutes. Participants were not compensated. As a part of the demographic information participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in Table 1. To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"). Participants were asked to confirm that they were participating the survey for the first time. Questions incorporating retrospective recall were all aligned to the period of "past four weeks".\
We conducted two rounds of data collection. At first, we collected data from `r nrow(EFA.descriptives)` participants (EFA sample). In the second round we collected data from another `r nrow(CFA.descriptives)` participants (CFA sample) making a total sample of `r nrow(desctable.data)`. The data analysed in this study was collected between 17 May 2021 and 3 September 2021.

@@

Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarize the response pattern of our total sample (n=`r nrow(sem.data)`) for all 48 items. Most of the items appeared skewed.The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated our data violated both univariate and multivariate normality. Multivariate skew was `r printnum(mardia.all.data$b1p)` (p \<0.001) and multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).

@@

In our CFA sample we had `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers. **Supplementary Table 5** summarizes the demographic descriptions native and non-native English speakers.Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models. The model fit did not significantly decrease across the nested models indicating the acceptability of the highest measurement invariance model: residual model.

@@

```{r InvarianceTab, results='asis'}
apa_table(Invariance.table, align = "c",  caption = "Measurment Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )

@@

## Developing Short form of LEBA: IRT Based Analysis
We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690). Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**). Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25, 30, 38, & 41) had relatively flat information curves (I($\theta$) \<.20). We discarded those items which yielded a short form of LEBA with 5 factors and 18 items (**Supplementary File 2**).

@@

We treated each factor of short-LEBA as a unidimensional construct and obtain 5 TICs (Figure \@ref(fig:Testinfo)). These information curves indicated except the first and fifth factors, the other three factor's TICs are roughly centred on the centre of the trait continuum ($\theta$). The first and fifth factor had a peak to the right side of the centre of latent trait.Thus we conferred the LEBA scale estimated the light exposure related behaviour with precision near the centre of trait continuum for 2nd, 3rd and 4th factors and near the right side of the centre of trait continuum for 1st and 5th factors [@bakerBasicsItemResponse2017].

@@

Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five factor structure we obtained in our EFA thus provided evidence of structural validity.(CFI=`r apa(fit.2[5],2,F)`; TLI=`r apa(fit.2[6],2,F)`); RMSEA=`r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR=`r apa(fit.2[10],2,F) `). However, in this model we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings. Also, we accepted one pair of items (item 30 $\&$ 41) to covary their error variance . This item-pair was capturing smart-watch based light exposure behaviour. In retrospect, it seemed plausible that not having  a smart-watch may lead the respondent to answer in a similar fashion for these two items. Thus, we decided to accept the modification to our model. The internal consistency coefficients ordinal alpha for the five factors and the total scale were also satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,F)`). On this same data set our measurement invariance analysis indicated the underlying construct of our scale "Light exposure related behaviour" was equivalent across native and non-native English speakers. This indicated the applicability of LEBA on both native and non-native English Speakers. However, this decisions brought up another question to be answered, what was the required grade level to understand the items of our scale? To answer this question we ran secondary analysis where we identified the grade level required using Flesch-Kincaid grade level identification method. Our scale would appear understandable to those who were at least a grade four student and had a age of at least 8.33 years. As a secondary analysis we also assessed the semantic similarity of our scale to the scales recorded in the "Semantic Scale Network" database [@rosenbusch2020semantic]. "LEBA" was  related to  "Sleep Disturbance Scale For Children" (SDSC) [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite]. Upon inspecting the item contents we found items under "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC and CIDI. However, the aim of those scale and ours were different. Items in those two scales were looking into behaviours related to sleep whereas our aim was to capture light exposure related behaviour.

lastly, we developed a short-LEBA (18 items) using IRT analysis. We fitted a graded response model model to the combined EFA and CFA sample (n=`r nrow(data)`). We discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20]. Test information curves indicated short form of LEBA is a psychometrically sound measure with adequate coverage of underlying traits to capture different extents of light exposure related behaviours with precision. Item fit index and person fit index for all five fitted model were acceptable providing evidence of validity of our models. Items had diverse item discrimination parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behaviour.

Based on all the gathered evidences, we can say LEBA can be used to profile individuals based on their light exposure related behaviours, which can facilitate the development process of individual interventions to promote health. All the five factors of LEBA may identify 'problematic' behaviours that are opposed to good light hygiene.

>>>>

A quantitative cross-sectional fully anonymous geographically unconstrained online large-scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch). Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic-book "Enlighten your clock" co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux]. The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation at any time without being penalized. At the beginning of the survey, for the adult participants (\>18 years) consent was recorded digitally. Under-aged participants (\<18 years) were urged to obtain assent from their parents/legal guardians. The entire survey was estimated to take less than 30 minutes. Participants were not compensated. As a part of the demographic information participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in Table 1. To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention. What is 4+5?"). Participants were asked to confirm that they were participating in the survey for the first time. Questions incorporating retrospective recall were all aligned to the period of "past four weeks".

We conducted two rounds of data collection. At first, we collected data from `r nrow(EFA.descriptives)` participants (EFA sample). In the second round we collected data from another `r nrow(CFA.descriptives)` participants (CFA sample) making a total sample of `r nrow(desctable.data)`. The data analysed in this study was collected between 17 May 2021 and 3 September 2021.

@@

Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarize the response pattern of our total sample (n=`r nrow(sem.data)`) for all 48 items. Most of the items appeared skewed. The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated our data violated both univariate and multivariate normality. Multivariate skew was `r printnum(mardia.all.data$b1p)` (p \<0.001) and multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).

@@

In our CFA sample we had `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers. **Supplementary Table 5** summarizes the demographic descriptions native and non-native English speakers. Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models. The model fit did not significantly decrease across the nested models indicating the acceptability of the highest measurement invariance model: residual model.

@@

```{r InvarianceTab, results='asis'}
apa_table(Invariance.table, align = "c",  caption = "Measurement Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )

@@

## Developing Short form of LEBA: IRT Based Analysis
We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690). Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**). Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25, 30, 38, & 41) had relatively flat information curves (I($\theta$) \<.20). We discarded those items which yielded a short form of LEBA with five factors and 18 items (**Supplementary File 2**).

@@

We treated each factor of short-LEBA as a unidimensional construct and obtain five TICs (Figure \@ref(fig:Testinfo)). These information curves indicated except the first and fifth factors, the other three factor's TICs are roughly centred on the centre of the trait continuum ($\theta$). The first and fifth factor had a peak to the right side of the centre of latent trait. Thus we conferred the LEBA scale estimated the light exposure related behaviour with precision near the centre of trait continuum for second, third and fourth factors and near the right side of the centre of trait continuum for first and fifth factors [@bakerBasicsItemResponse2017].

@@

Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five factor structure we obtained in our EFA thus provided evidence of structural validity.(CFI=`r apa(fit.2[5],2,F)`; TLI=`r apa(fit.2[6],2,F)`; RMSEA=`r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR=`r apa(fit.2[10],2,F) `). However, in this model, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings. Also, we accepted one pair of items (item 30 $\&$ 41) to covary their error variance . This item-pair was capturing smart-watch based light exposure behaviour. In retrospect, it seemed plausible that not having  a smart-watch may lead the respondent to answer in a similar fashion for these two items. Thus, we decided to accept the modification to our model. The internal consistency coefficients ordinal alpha for the five factors and the total scale were also satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,F)`). On this same data set our measurement invariance analysis indicated the underlying construct of our scale "Light exposure related behaviour" was equivalent across native and non-native English speakers. This indicated the applicability of LEBA on both native and non-native English Speakers. However, this decisions brought up another question to be answered, what was the required grade level to understand the items of our scale? To answer this question we ran secondary analysis where we identified the grade level required using Flesch-Kincaid grade level identification method. Our scale would appear understandable to those who were at least a grade four student and had a age of at least 8.33 years. As a secondary analysis we also assessed the semantic similarity of our scale to the scales recorded in the "Semantic Scale Network" database [@rosenbusch2020semantic]. "LEBA" was  related to  "Sleep Disturbance Scale For Children" (SDSC) [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite]. Upon inspecting the item contents we found items under "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC and CIDI. However, the aim of those scale and ours were different. Items in those two scales were looking into behaviours related to sleep whereas our aim was to capture light exposure related behaviour.

lastly, we developed a short-LEBA (18 items) using IRT analysis. We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`). We discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20]. Test information curves indicated short form of LEBA is a psychometrically sound measure with adequate coverage of underlying traits to capture different extents of light exposure related behaviours with precision. Item fit index and person fit index for all five fitted model were acceptable providing evidence of validity of our models. Items had diverse item discrimination parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behaviour.

Based on all the gathered evidence, we can say LEBA can be used to profile individuals based on their light exposure related behaviours, which can facilitate the development process of individual interventions to promote health. All the five factors of LEBA may identify 'problematic' behaviours that are opposed to good light hygiene.
